intro

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort [@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve goals.

However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED) [@Westbrook2013].

## 1.1 ER strategy discounting
<!-- NHB template says that there should not be subheadings in the introduction -->
In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm.", out.width="98%"}
include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
```
## 1.2 The present study

>>>>

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort [@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve ER goals.

However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED) [@Westbrook2013].

## 1.1 ER strategy discounting
<!-- NHB template says that there should not be subheadings in the introduction -->
In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption taht teh objectively easiest *n*-back level has the highest SV.
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm.", out.width="98%"}
include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
```
## 1.2 The present study
